Reproduction frequency and offspring survival decline in elephant seals past prime age

### 2024-10-15 paper/paperv3.qmd
Updating pop dynamics equation notation

$$
\pi_{1a} = \frac{\sum_{a=4}^{20} b_a n_a}{\sum_{a=4}^{20} n_a}
$$

Where $\pi_1$ is pup production per mother per year by the age-structured population. $a$ is age, $b$ is estimated breeding percentage, and $n$ is the number of mothers in that age class.

@@

$$
\pi_{2a} = \frac{\sum_{a=4}^{11} b_a n_a + \sum_{a=12}^{20} b_{11} n_a}{\sum_{a=4}^{20}n_a}
$$

@@

Similarly, the observed and hypothetical quantity of pups that survive to adulthood adds a term $s$ for offspring survival.

$$
\pi_{1b} = \frac{\sum_{a=4}^{20} b_a n_a s_a}{\sum_{a=4}^{20} n_a}
$$

$$
\pi_{2b} = \frac{\sum_{a=4}^{11} b_a n_a s_a + \sum_{a=12}^{20} b_{11} n_a s_{11}}{\sum_{a=4}^{20} n_a}
$$

>>>>

$$
F_{1} = \frac{\sum_{a=4}^{20} b_a n_a}{\sum_{a=4}^{20} n_a}
$$

Where $F$ represents fertility, described by pup production per mother per year by the age-structured population. $a$ is age, $b$ is estimated breeding percentage, and $n$ is the number of mothers in that age class.

@@

$$
F_{2} = \frac{\sum_{a=4}^{11} b_a n_a + \sum_{a=12}^{20} b_{11} n_a}{\sum_{a=4}^{20}n_a}
$$

@@

Similarly, to account for the influence of maternal effects ($M$), we add a term $s$ for offspring survival to estimate the observed and hypothetical quantity of pups that survive to adulthood.

$$
M_{1} = \frac{\sum_{a=4}^{20} b_a n_a s_a}{\sum_{a=4}^{20} n_a}
$$

$$
M_{2} = \frac{\sum_{a=4}^{11} b_a n_a s_a + \sum_{a=12}^{20} b_{11} n_a s_{11}}{\sum_{a=4}^{20} n_a}
$$
